Environmental Dependence of the Structures of Massive Central Galaxies at $z=0.4$ ....... or ... A Detection of the Enviromental Dependence of The Stellar Halos of Massive Galaxies

### 2017-01-16 draft/ms_v2.tex
New Tex draft

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\input psfig.tex

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}

@@

\title{First Detection of the Environmental Dependence of the Structures of Massive Galaxies }

@@

    Although the environmental dependence of structures for massive central 
    galaxies is predicted by the promising hierarchical assembly model, 
    observations at low redshift seem to find no convincing evidence for that. 
    With the help of deep $i$-band images of a large sample of massive central 
    galaxies at $0.3 < z < 0.5$ from the Subaru Hyper Suprime-Cam (HSC) survey, 
    we map their stellar mass distributions out to radius larger than $100$ kpc, 
    and discover subtle, but systematic and robust structural differences that 
    depend on halo mass. 
    At fixed stellar mass within 100 kpc, the massive central galaxies in more 
    massive ($M_{200m} > 1.6\times 10^{14} M_{\odot}$) halos have a 
    slightly flattened inner profile within $\sim 15$-$20$ kpc, and a more prominent 
    outer envelope compared to ones in less massive 
    ($M_{200m}>8.7\times 10^{13} M_{\odot}$) halos.
    For centrals with $M_{\star} > 10^{11.5} M_{\odot}$, the ones in more massive 
    halos show very significant excess of mass in the outskirt when the two samples 
    are matched using proxies of mass assembled at $z > 1$. 
    Such differences are broadly consistent with richer recent merging history 
    for more massive halos. 
    We suggest that the relation between total stellar mass and mass within inner 5 
    or 10 kpc is potentially interesting for diagnosing the role played by host halo 
    in shaping the structures of massive central galaxies. 
    These results also highlight the importance of deep photometry and the usage of 
    detailed structural information in the study of the assembly history of galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{Three-color images for a subsample of massive galaxies at similar redshift
      		($\sim 0.4$), and with similar \mstar{} inside inner 10 kpc (indicated by the 
            dash-line cicle on top-left figure; 
            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
            However, they span quite a large range in \mstar{} within 100 kpc 
            (highlighted by the solid bar on the top-left figure). 
            From top-left to bottom-right, their \mtot{} increases from 
            $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$.
            The three galaxies from \rbcg{} sample are highlighted via red frames.
            }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[bt]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile in $R^{1/4}$ scale as it 
            is the most appropriate one to show the structural details of massive 
            ETGs at both inner and outer regions. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the brightness profile of the PSF model normalized at the 
            central surface brightness of the galaxy to highlight the region affected 
            by seeing. 
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote.~~~ 
            Right: the masked $i$-band image of this galaxy with the isophotes extracted 
            by \texttt{Ellipse} overlaid. 
            The thick, green isophote highlights the one with $\mu_{i}\sim 28.5$~\sb.}
            \song{Will update completely, takes a little bit longer}
            %\alexie{Can we add physical radii at the top left since $R^{1/4}$ is not 
            %    very intuitive. On the right hand side, why show the background as blue, 
            %    instead of showing the actual image of the galaxy with masks overlaid? 
            %    Add units to x axis of right hand side. 
            %    Red text on left hand side, replace with "1D profile of a $10^{xx}$ 
            %    M$_{\odot}$ galaxy at $z=xx$}.}
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru telescope at 
    Mauna Kea. 
    This ambitious multi-layer photometric survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of HSC and will cover $\sim 1400$ deg$^2$ of sky in 5
    broad bands (\textit{g r i z Y}) to the depth of $r \sim 26$ mag in the \texttt{WIDE}. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$square of degree of sky in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

   The HSC \texttt{WIDE} survey is $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (median $i$-band seeing is 0.6"), 
    and the wide area, this makes the HSC wide layer a tremendous data set to perform a 
    large statistical study of surface brightness profiles of ETGs out to large radii. 
    Fig.\ref{fig:sdss_compare} illustrated the quality of HSC imaging compared to SDSS 
    for a sample of low redshift ETGs. 
    Fig.\ref{fig:sdss_compare} clearly demonstrates that the HSC Wide survey is well 
    suited for mapping the stellar distribution of massive galaxies out to large radii 
    and will be a powerful data set to explore the assembly history of ETGs.

	The HSC $i$-band images typically have the best seeing in all five bands because of 
    strict requirements determined by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{The HSC galaxy catalog and photometry measurements}
    \label{sec:pipeline}

    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
    Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Then pipeline perform astrometric and photometric calibration for each single 
    expoures. 
    After that, the \texttt{hscPipe} warp different exposures on to a common
    World Coordinate System (WCS), combine them into coadded images with improved 
    signal-to-noise ratio ($S/N$), and update the images with better astrometric and 
    photometric calibrations at the same time using the common stars among different
    exposures.
    The pixel scale of the combined images is $0.168^{\arcsec}$.  
    The photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. 
    First, the \texttt{hscPipe} performs object detection again on the coadd images
    in each band independently, and identify the above-threshold region (referred as 
    ``footprint'') and the flux peak within it for each source. 
    ``footprints'' and peaks from different bands are then merged together before 
    the \texttt{hscPipe} deblend and measure them in each band. 
    Later, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, it is the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band.
    The PSF and galaxy model fluxes measured in the forced photometry approach are the
    best for color measurements.  
    Please refer to \citet{BoschInPrep} for more details of the \texttt{hscPipe} and 
    the multi-band processing method.

    The HSC \cmodel{} algorithm is similar to the SDSS \cmodel{} one.  
    It fits the flux distribution of an object using a combination of de~Vaucouleur and 
    exponential components after considering the PSF convolution.  
    For more details about the algorithm, please see Bosch\etal~in prep.~.
    We have tested its performance using synthetic objects (Huang\etal~in prep.~), and 
    the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
    accurate down to $i >25.0$ mag.  
    However, for massive ETGs with extended stellar distributions, \cmodel{} currently 
    systematically underestimates their total flux.
    This problem indicates the intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles that are extremely extended in the outskirt at the depth of 
    HSC survey. 
    At the same time, issues with the deblender also worsen the situation. 
    As the image becomes much deeper, it also significantly increases the fraction 
    objects that are blended with others, and makes reliable deblending process 
    a very challenging problem especially for massive ETGs where satellites and 
    background galaxies often blend with the low surface brightness stellar envelope.
    To make sure the reliable detection of faint objects close to the detection limit, 
    the deblending method implemented by the \texttt{hscPipe} now tends to 
    ``over-deblend'' the surrounding areas of bright galaxies, and further results in 
    under-estimated total flux of massive ETGs (more discussion in 
    Bosch\etal~in prep.~).  
    For these reasons, we will perform customized photometric measurements to derive 
    more accurate total luminosity and stellar mass. 
    We only use the HSC \cmodel{} photometry in the initial selection of parent 
    sample.

@@

    Because of the caveats that apply to \texttt{hscPipe} measurements for bright 
    galaxies, we will use custom made software to measure the luminosity profiles of
    massive galaxies. 
    \update{
    As the first step, we select the initial sample of massive galaxies at $z < 0.5$
    from the HSC photometric catalog.}
    We will then use custom made software to re-measure luminosities for all galaxies 
    in this sample. 
    Based on Leauthaud\etal~(2016), most \logms{}$\geq 11.5$ galaxies should have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag.
    So we first select all galaxies with $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters}
    in regions that have reached the required depth of \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We select extended objects that have no error in deblending process, well defined 
    centroids, and \texttt{cModel} magnitudes in all five bands. 
    After removing the objects that have pixel affected by saturation, cosmic-ray, and 
    other optical artefact \footnote{each criterion affects less than 8\% of the entire
    sample}, we select 1760845 galaxies that will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    As reliable photometric redshift using HSC photometry is still a working progress, 
    we only use objects with either available spectroscopic redshift or robust 
    red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We first match the \texttt{hscPho} sample with the external spec-$z$ catalog 
    compiled by the HSC database\footnote{It is created by matching HSC objects with 
    public data of several spectroscopic surveys (e.g.\ SDSS/BOSS; GAMA). 
    Duplicated matches from different sources are merged through internal matching 
    using $0.5^{\arcsec}$ radius. 
    For each object, the quality information of the spec-$z$ from different catalogs 
    are homogenized into a single flag that indicates whether the redshift is secure, 
    and only secure spec-$z$ are used in this work.}
    %% This is catalog: "dr1_specz_use.fits"
    using $1.0^{\arcsec}$ radius.
    At $0.2 \leq z \leq 0.5$, most redshifts in the HSC spec-$z$ catalog come from 
    SDSS/BOSS and GAMA surveys.  
    The BOSS survey provides the majority of spec-$z$ in this work.  
    Due to the complex selection criteria for different subsamples within the BOSS
    survey (e.g.\ the \texttt{LOWZ} and \texttt{CMASS}), it is not easy to estimate 
    its \mstar{} completeness.  
    Recently, through comparing with the deeper Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} suggests that the 
    BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprint, provides 
    additional 14\% unique spec-$z$. 
    Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. 
    Despite the difference in \mstar{} estimates, we can expect 
    our sample should be quite complete above \logms{}$\geq 11.5$-$11.6$.
    We will further address the issue of \mstar{}-completeness more carefully 
    using the common sample with \texttt{S82-MGC} (see Section\ref{ssec:s82}).

    Among the 116813 matched objects, 42696 are at $0.2 \leq z \leq 0.5$.
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of these redshifts come from either SDSS or BOSS data.  
    GAMA survey contributes another $\sim 14$\%. 
    For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).
    As we will mention at the end of the paper, to ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end, and make sure the samples we 
    want to compare have well overlapped redshift distributions, we will focus on 
    the galaxies at $0.3 \leq z \leq 0.5$.

@@

    In this paper, our study focuses on galaxies which are located at the center of
    their dark matter halos. To limit our sample to central galaxies, we use 
    \texttt{v5.10} of the \redm{}{} cluster 
    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has been 
    run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
    a richness $\lambda$, and identified the most likely central
    galaxy (this is the galaxies with the highest value of the central probability 
    $P_{\mathrm{Cen}}$). 
    A list of member galaxies for each cluster, and associated membership probabilities, 
    is also provided. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
    \citealt{Simet2016}). 
    The results of these studies are in good agreement and indicate that clusters 
    identified by \redm{}~($\lambda > 20$) have $\log (M_{200,c}/M_{\odot}) \geq 14.0$. 
    Therefore, the \redm{} catalog helps us group the massive central galaxies into 
    samples with different average \mhalo{}.  
    And, to select reliable candidates of central galaxies, we only include the ones 
    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$).

    Although the \redm{} catalog provides us a good sample of central galaxies in 
    massive halos, the typical uncertainty of $\lambda$ estimate is still at 
    $\sim 5$-10 level.  
    In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
    becomes slightly incomplete at lower richness ($\lambda < 40$) end at $z > 0.33$.
    To reduce the impacts from uncertain richness and incomplete selection of 
    massive halos, we will focus on a sample of central galaxies in halos with 
    $\lambda > 30$. 
    This will also help up enhance the \mhalo{} contrast in the structural comparison.     
    Based on the calibration in \citet{Simet2016}, the $\lambda \geq 20$ sample should
    have halo mass ($M_{200m}$) more massive than $10^{14.0} M_{\odot}$.  
    For the $\lambda \geq 30$ sample, they should live in halo more massive than
    $10^{14.2} M_{\odot}$ using the same calibration. 
    And, we can confirm that the results presented later do not depend on the choice 
    of $\lambda$ boundary here. 
    For the massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.     
    %\textcolor{red}{but sometimes we make cuts at $\lambda<20$ and $\lambda>30$. 
    %Is it confusing to have several different thresholds? Need to give a Motivation 
    %for using different numbers here.}

>>>>

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

@@

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\rewrite}[1]{\textcolor{green}{\textbf{[Rewrite: #1]}}}

\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
%\newcommand{\update}[1]{#1}

@@

\title{Environmental Dependence of the Structures of Massive Central 
       Galaxies at $z=0.4$ ....... or ... A Detection of the Enviromental Dependence of The Stellar Halos of Massive Galaxies}

@@

    The promising hierarchical assembly scenario of massive galaxies suggest the 
    structure of these galaxies should depend on their environments or halo mass.
    Yet, at low redshift, observations find no clear evidence for that. 
    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
    out to the very outskirt, and detect subtle, but robust structural differences 
    that depend on halo mass for central galaxies at high mass end. 
    With the help of the \redm{} catalog, we separate these massive galaxies 
    into centrals of halos that are more and less massive than 
    $M_{200m}\sim 10^{14} M_{\odot}$.
    For centrals with similar stellar mass within 100 kpc, the ones from 
    more massive halos on average have slightly more flattened inner profile 
    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
    proxy of the mass of the in-situ component, the massive centrals of more  
    massive halos show much more significant outer stellar envelopes.    
    We also see that these two samples of massive galaxies follow slightly 
    different mass-size relation and the relationship between the stellar mass 
    within 100 and 10 kpc.
    Such differences in structure are broadly consistent with the expectation that
    central galaxy from more massive halo should have more complex merging history.
    These results highlight the importance of deep photometry in the study of 
    the assembly history of massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}[t!]
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and with similar values for their stellar masses within a fixed 10 kpc radius (indicated by the 
            dash-line cicle on top-left figure; 
            $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). Galaxies are rank ordered from top to bottom and from left to right by their mass within 100 kpc which varies from $10^{11.2} M_{\odot}$ to $10^{11.7} M_{\odot}$. At fixed "inner" mass $M_{\star,10}$, massive galaxies display a large diversity in their outer profiles. Red boxes indicate galaxies in halos more massive then xxxxx. }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}[bt]
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling on the x-axis. By using this scaline, ETGs that follow exact de Vaucouleurs profiles with have luminosity profiles that appear on stright lines in our Figures. The dash-line shows the surface brightness profile after correcting the background \alexie{no dashed line?}. We also plot the brightness profile of the PSF model normalized at the 
            central surface brightness of the galaxy to highlight the region affected 
            by seeing. The grey shaded region highlights the region most affect by seeing ($r<$xxx kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. Right: the masked $i$-band image of this galaxy with the isophotes extracted 
            by \texttt{Ellipse}. The thick dotted line highlights the isophote with $\mu_{i}\sim 28.5$~\sb.}
            %\alexie{Can we add physical radii at the top left since $R^{1/4}$ is not 
            %    very intuitive. On the right hand side, why show the background as blue, 
            %    instead of showing the actual image of the galaxy with masks overlaid? 
            %    Add units to x axis of right hand side. 
            %    Red text on left hand side, replace with "1D profile of a $10^{xx}$ 
            %    M$_{\odot}$ galaxy at $z=xx$}.}
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    The Subaru Strategic Program (SSP, \addref) makes use of the new prime-focus camera,
    the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 8.2-m Subaru telescope at 
    Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ in 5
    broad bands (\textit{g r i z Y}) to a limting depth of $r \sim 26$ mag in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$square of degree in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

   The HSC \texttt{WIDE} survey is $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
    and the wide area, the HSC survey represents a tremendous data set to perform a 
    large statistical study of the surface brightness profiles of ETGs out to large radii. Fig.\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for a sample of low redshift ETGs and shows that HSc survey data are well 
    suited for mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing comapred to other bands because of 
    strict requirements driven by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC Data Processing}
    \label{sec:pipeline}

The full details of the HSC data processing can be found in \citet{BoschInPrep} and are briefly summarized here. The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the Large 
    Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). Astrometric and photometric calibration is performed at the single exposure level. \texttt{hscPipe} then warps different exposures on to a common
    World Coordinate System (WCS) and combines them into coadded images. At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among between exposures.

    The pixel scale of the combined images is $0.168^{\arcsec}$. Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. First, \texttt{hscPipe} performs object detection on coadd images
    in each band independently and for each source records the flux peak and the above-threshold region (referred as 
    a ``footprint''). Next, ``footprints'' and peaks from different bands are merged together before performing deblending and measurements. Finally, \texttt{hscPipe} selects a ``reference band'' for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band. This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach that is similar to SDSS (\ref{}) (Bosch\etal~in prep.~). However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which means that it can be used to accurately measure both the \textit{fluxes and colors of galaxies}. The HSC \cmodel{} algorithm fits the flux distribution of each object using a combination of a de~Vaucouleur and 
    an exponential component and accounts for the PSF. The performance of this algorithm has been testing using synthetic objects (Huang\etal~in prep.~) and 
    the results indicate that, generally speaking, the HSC \cmodel{} photometry is 
    accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of massive ETGs with extended stellar distributions. This problem indicates an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated at the depth of 
    the HSC survey. In addition, at the depth of the HSC survey, accurate deblending in the vicinity of large ETGs where satellites and background galaxies often blend with the low surface brightness stellar envelope is a challenign problem. The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to un under-estimation of the the total flux of massive ETGs (more discussion in 
    Bosch\etal~in prep.~).  For these reasons, our results will be based on custom developed code to measure the luminosities and stellar masses of massive galaxies. We use the HSC \texttt{hscPipe} photometry for two purposes: 1) to perform a first broad sample selection, and 2) for galaxy colors. \alexie{Shouldn't we be using the aperture photometry here ???? Are we doing teh right thing here?? Please check. Need a simple sanity check to show that the resutls are robust. Check using your own color estimates?}.

@@

    \alexie{Try to be more succinct and improve the logical flow in sections 2.3, 2.4, and 2.5. Readers don't care about the process! You should be able to trim these sections.}

    \alexie{We never say anything about Spirals? Are all galaxies in this selection early types? Are there any extra morphology cuts? We need to mention this somewhere.}

    \update{
    We begin by using a broad luminosity cut to select an initial sample of massive galaxies at $z < 0.5$
    from the HSC photometric catalog.} Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. We therefore select our initla smaple to be brighter than  $i_{\mathrm{HSC, cModel}} \leq 21.5$ 
    \footnote{We neglect the insignificant differences between the response curves of
    SDSS-$i$ and HSC-$i$ filters} and also limit our sample to regions that have reached the required depth of the \texttt{WIDE} survey in all 
    five bands. 
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artefact \footnote{each criterion removes less than 8\% of the entire
    sample} \alexie{Actually, 8 percent is not small if we want to condsider the number densities. Let's re-evaulate the impact of these cuts for the 16B data with FDFC}. This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}.

    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    We limit our study to the very high mass end where a majority of galaxies have either a  spectroscopic redshift or a robust 
    red-sequence photo-$z$ from the \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog 
    compiled by the HSC team\footnote{It is created by matching HSC objects with all publicly available spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from different catalogs 
    are homogenized into a single flag that indicates whether the redshift is secure (\ref{} Cite a paper from the photo team where this is described?). Only galaxies with secure spec-$z$s are used in this work \alexie{Ned to be precise here. We also use redshifts from redmapper so this statement isn;t quite right}}.  To ensure reasonable 
    \mstar{}-completeness at the high-\mstar{} end we focus on the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

        \alexie{Please rewrite the section below. It would be better to first say that you further supplements with redmapper redshifts. And then simply quote the overall number at the end after making the redshift cut. Need to work on logical flow of text!}.

  In addition to the specz-s mentioned above, we also include objects which have a red-sequence photo-$z$ from the \redm{} catalog within the range $0.2 \leq z \leq 0.5$ .........and need to say one sentance about the accuracy of the red sequence redshifts and why this is tolerable for our work

    \rewrite{For objects without external spec-$z$, we match them with the central galaxies 
    from \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.2 \leq z \leq 0.5$
    (will be referred as \texttt{hscZ}).   From our initial sample, 42696 are at $0.2 \leq z \leq 0.5$.}
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"

    The BOSS and SDSS "legacy" LRG samples provide the majority of spec-$z$ for this work. By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the stellar mass completness of the combined BOSS and SDSS samples. They estimate that the BOSS spec-$z$ is about 80\% complete at \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. The GAMA survey, which partially overlaps with the HSC footprint, supplements our spec-z sample by 14\%. \alexie{and redmapper redshifts add another xx percent.} Based on \citet{Taylor2011} (e.g.\ their Fig.~6), at $z\sim 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z\sim 0.5$. We can therfore expect our sample to be roughly stellar-mass complete above \logms{}$\geq 11.5$-$11.6$. This question will be addressed more carefully using the overlap region between HSC and the \texttt{S82-MGC} in Section\ref{ssec:s82}.

@@

    Our study focuses on galaxies which are located at the center of
    their dark matter halos. To limit our sample to central galaxies, we use 
    \texttt{v5.10} of the \redm{}{} cluster 
    catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has been 
    run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift estimate $z_{\lambda}$, 
    a richness $\lambda$, and identifies the most likely central
    galaxy (this is the galaxy with the highest central probability value
    $P_{\mathrm{Cen}}$). The \redm{}{} catalog also provides a list of member galaxies for each cluster and associated membership probabilities. Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015}; \citealt{Farahi2016}; 
    \citealt{Simet2016}). 
    The results of these studies are in good agreement and indicate that clusters 
    identified by \redm{}~ with $\lambda > 20$ have $\log (M_{200m}/M_{\odot}) \geq 14.0$. 
    Therefore, the \redm{} catalog helps us group massive central galaxies into samples with different average \mhalo{}. \alexie{Here is looks like you are making a cut on pcen. But what about galaxies that are not in these clusters? You do not have a pcen value! So this phrase needs to be rewritten or moved elsewhere.}\rewrite{To select reliable candidates of central galaxies, we only include the ones 
    with high probability of being the central galaxy ($P_{\mathrm{CEN}} \geq 0.7$)}.

    Although the \redm{} catalog provides us a good sample of central galaxies in 
    massive halos, the typical uncertainty of $\lambda$ estimate is still at the
    $\sim 5$-10 level.  
    In addition, due to the depth and resolution of SDSS images, the \redm{} catalog 
    becomes slightly incomplete at lower richness ($\lambda < 40$) at $z > 0.33$.
    To reduce the impact of this effect, we will focus on a sample of central galaxies in halos with 
    $\lambda > 30$. 
    Based on the calibration of \citet{Simet2016}, the $\lambda \geq 30$ sample should
    have halo mass ($M_{200m}$) more massive than $10^{14.2} M_{\odot}$. We have checked that none of our results depend on this choice of the $\lambda$ boundary.

    For the massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they should have $\log (M_{200m}/M_{\odot}) < 14.0$.
